---
title: "Exercise 3.3.1"
---
```{r}
install.packages("tidyverse")
library(tidyverse)
```

1) What’s gone wrong with this code? Why are the points not blue?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```


2) Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?
```{r}
?mpg
```

```{r}
head(mpg, 1)
```
Categiorical variables are ones with a limited size include: <chr> character
continous have an infinite number includes: <int> integer and <dbl> double


3) Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?
```{r}
ggplot(data=mpg) +
  geom_point(mapping = aes(x=displ, y=hwy, color=cyl, size=hwy, shape= drv))
```


4)What happens if you map the same variable to multiple aesthetics?
There both displayed 

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = cyl, size = cyl))
```

```{r}
ggplot(data=mpg) + geom_point(mapping=aes(x=displ, y=hwy, color= drv, shape=drv))
```


5)What does the stroke aesthetic do? What shapes does it work with?
It increases the sizes of the shapes
```{r}
ggplot(data=mpg) +
  geom_point(mapping = aes(x=displ, y=hwy, color=cyl, size=hwy, shape= drv, stroke=5))
```

6)What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? 
It applies to the evaluated value 
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, colour = displ < 5))
```





